Efficient Community Formation \\ for Web Services

### 2013-12-21 papers/coalition-journal-R1/coalition_journal_r1.tex
changes

\emph{2) Master Web Services} or the community coordinators, are
representatives of the communities of web services and responsible
for their management. Communities receive requests from users and
aim to host a healthy set of web services to perform the required
tasks. They seek to maximize user satisfaction by having tasks
accomplished according to the desired QoS. In fact, higher user
satisfaction will bring more user requests and increase the market
share and revenue of the community.

@@

Figure \ref{fig_community} represents the architecture of web
service communities. The community is essentially a virtual group
of web services having similar and complementary functionalities.
Communities aggregate web services and communicate with other
entities such as UDDI registries and users, using identical
protocols as single web services. Web services join communities to
increase their utility by having a larger market share and task
pool. Community coordinators or master web services are
responsible for community development, managing membership
requests from web services and distributing user tasks among the
community members. Community coordinators try to attract quality
web services for joining and keep the community as stable and
productive as possible to gain better reputation and user
satisfaction, which results in having a higher market share for
the community. The way the web services reside inside communities
and how communities of web services are engineered is described
comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}.

@@

As mentioned in Section \ref{webservice-communities}, communities
are robust service providers with well established market share
and reputation. By maintaining their reputation and performance,
they attract  end users which choose them as service providers to
perform their tasks. The community master is characterized by a
request rate (also called input rate) $(R_C)$ from users. Each web
service comes with a given QoS ($QoS_{ws}$) from which the
throughput $Th_{ws}$ is excluded. Throughput is the average rate
of tasks a web service can perform per time unit. Its exclusion
from $QoS_{ws}$ allows us to build our analysis on the particular
value of $Th_{ws}$. Thus, web services perform tasks with an
average output quality of $QoS_{ws}$ and a throughput rate of
$Th_{ws}$.

The community master uses a slightly modified \emph{weighted fair
queuing} method to distribute tasks among its members. The goal is
to allocate incoming tasks to web services with a rate matching
the throughput value of $Th_{ws}$. In the \emph{weighted fair
queuing} method, \emph{all} the input flow is multiplexed along
different paths, however in our case if the request rate $(R_C)$
of the community is more than the summation of throughput values
of the web services in the community, some of the input tasks will
be queued and served with delay. Thus, the amount of tasks
performed by the community is $\sum_{ws}{Th_{ws}}$ when
$\sum_{ws}{Th_{ws}} \leq R_{C}$. However, when the input rate
$(R_C)$ of the community is less than the summation of throughput
values of the web services in the community,
%the community has more web services having more total throughput value than community's request rate
the \emph{weighted fair queuing} algorithm assigns a weighted task
rate of $R_C \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ for each
web service ($ws$), so that the total rate of tasks being
performed is $R_C$, the community's request rate.

While distributing tasks, the community master can verify the
performance, throughput and quality of service of tasks being
performed by web services. The master can recognize if those web
services are capable of doing the amount of tasks they advertised.
If for any reason there is a decline in the quality metric or
throughput, the master will announce the new parameters, which
will be considered as benchmark for future performance
calculations, and penalize the suspicious web services. In this
way, players will have incentive to truthfully reveal their real
capabilities in order to profit best from the community and to
avoid being penalized. In addition, the system should be dynamic
enough to detect and react to web services quality metrics
variation as over time web service metrics may degrade or improve,
a change that the community should adjust to.
% Therefore its easy for the system to encourage players to be in some sense incentive compatible in the way that they would profit best by truthfully revealing their capabilities. Also it is important to be dynamic enough to consider web services which may have their quality metrics degraded or even improved over time for any reason and be able to adjust the community with new parameters.

>>>>

\emph{2) Community coordinators} are
representatives of the communities of web services and responsible
for their management. Communities receive requests from users and
aim to host a healthy set of web services to perform the required
tasks. They seek to maximize user satisfaction by having tasks
accomplished according to the desired QoS. In fact, higher user
satisfaction will bring more user requests and increase the market
share and revenue of the community.

@@

Figure \ref{fig_community} represents the architecture of web
service communities. The community is essentially a virtual group
of web services having similar and complementary functionalities.
Communities aggregate web services and communicate with other
entities such as UDDI registries and users, using identical
protocols as single web services. Web services join communities to
increase their utility by having a larger market share and task
pool. Community coordinators are
responsible for community development, managing membership
requests from web services and distributing user tasks among the
community members. Community coordinators try to attract quality
web services for joining and keep the community as stable and
productive as possible to gain better reputation and user
satisfaction, which results in having a higher market share for
the community. The way the web services reside inside communities
and how communities of web services are engineered is described
comprehensively in \cite{DBLP:journals/ijebr/MaamarSTBB09}.

@@

As mentioned in Section \ref{webservice-communities}, communities
are robust service providers with well established market share
and reputation. By maintaining their reputation and performance,
they attract  end users which choose them as service providers to
perform their tasks. The community coordinator is characterized by a
request rate (also called input rate) $(R_C)$ from users. Each web
service comes with a given QoS ($QoS_{ws}$) from which the
throughput $Th_{ws}$ is excluded. Throughput is the average rate
of tasks a web service can perform per time unit. Its exclusion
from $QoS_{ws}$ allows us to build our analysis on the particular
value of $Th_{ws}$. Thus, web services perform tasks with an
average output quality of $QoS_{ws}$ and a throughput rate of
$Th_{ws}$.

The community coordinator uses a slightly modified \emph{weighted fair
queuing} method to distribute tasks among its members. The goal is
to allocate incoming tasks to web services with a rate matching
the throughput value of $Th_{ws}$. In the \emph{weighted fair
queuing} method, \emph{all} the input flow is multiplexed along
different paths, however in our case if the request rate $(R_C)$
of the community is more than the summation of throughput values
of the web services in the community, some of the input tasks will
be queued and served with delay. Thus, the amount of tasks
performed by the community is $\sum_{ws}{Th_{ws}}$ when
$\sum_{ws}{Th_{ws}} \leq R_{C}$. However, when the input rate
$(R_C)$ of the community is less than the summation of throughput
values of the web services in the community,
%the community has more web services having more total throughput value than community's request rate
the \emph{weighted fair queuing} algorithm assigns a weighted task
rate of $R_C \times \frac{Th_{ws}}{\sum_{ws}{Th_{ws}}}$ for each
web service ($ws$), so that the total rate of tasks being
performed is $R_C$, the community's request rate.

While distributing tasks, the community coordinator can verify the
performance, throughput and quality of service of tasks being
performed by web services. The community coordinator can recognize if those web
services are capable of doing the amount of tasks they advertised.
If for any reason there is a decline in the quality metric or
throughput, the coordinator will announce the new parameters, which
will be considered as benchmark for future performance
calculations, and penalize the suspicious web services. In this
way, players will have incentive to truthfully reveal their real
capabilities in order to profit best from the community and to
avoid being penalized. In addition, the system should be dynamic
enough to detect and react to web services quality metrics
variation as over time web service metrics may degrade or improve,
a change that the community should adjust to.
% Therefore its easy for the system to encourage players to be in some sense incentive compatible in the way that they would profit best by truthfully revealing their capabilities. Also it is important to be dynamic enough to consider web services which may have their quality metrics degraded or even improved over time for any reason and be able to adjust the community with new parameters.
